---
title: "Day4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


# part1

6 digit number
two adjacent digits are the same (like 22 in 122345)
only ever increase or stay the same
e.g.
111111
How many different passwords within the range?
178416 to 676461


```{r}
meet_reqs = function(x){
  p1 = stringr::str_sub(x, 1,1) %>% as.numeric()
  p2 = stringr::str_sub(x, 2,2) %>% as.numeric()
  p3 = stringr::str_sub(x, 3,3) %>% as.numeric()
  p4 = stringr::str_sub(x, 4,4) %>% as.numeric()
  p5 = stringr::str_sub(x, 5,5) %>% as.numeric()
  p6 = stringr::str_sub(x, 6,6) %>% as.numeric()
  
  if(p1 == p2 | p2 == p3 | p3 == p4 | p4 == p5 | p5 == p6){
    cont = 1
  } else {
    cont = 0
    ans = 0
  }
  
  
  if(cont == 1 & (p6 >= p5 & p5 >= p4 & p4 >= p3 & p3 >= p2 & p2 >= p1)){
    ans = 1
  } else {
    ans = 0
  }
  
  return(ans)
  
}
```



```{r}

passwords = seq(178416, 676461) %>% 
  enframe(name = NULL) %>% 
  dplyr::rowwise() %>% 
  mutate(valid_pwd = map(value, meet_reqs))

```


```{r}

valid_passwords = passwords %>% 
  unnest() %>% 
  filter(valid_pwd == 1)

valid_passwords

```



```{r}

valid_passwords %>% 
  count(valid_pwd)

```


# part 2
An Elf just remembered one more important detail: the two adjacent matching digits are not part of a larger group of matching digits.

Given this additional criterion, but still ignoring the range rule, the following are now true:

112233 meets these criteria because the digits never decrease and all repeated digits are exactly two digits long.
123444 no longer meets the criteria (the repeated 44 is part of a larger group of 444).
111122 meets the criteria (even though 1 is repeated more than twice, it still contains a double 22).

112345

```{r}

meet_reqs2 = function(x){
  
  x1 = x %>% 
    as.character() %>% 
    stringr::str_split("") %>% 
    unlist() %>% 
    enframe(name = NULL) %>% 
    mutate(value = as.numeric(value),
           lag_value = lag(value),
           diffval = value - lag_value) %>% 
    drop_na %>% 
    mutate(no_diff = case_when(diffval == 0 ~ 1,
                               TRUE ~ 0)) %>% 
    filter(no_diff > 0) %>% 
    group_by(value) %>% 
    summarise(num_consec = sum(no_diff)) %>% 
    select(num_consec) %>% 
    min()
  
  if(x1 == 1){
    ans = 1
  } else {
    ans = 0
  }
    
  return(ans)

}
  
```


```{r}

x = 112233 # should be yes

x = 123444 # should be no

x = 111122 # should be yes

x = 112345 # shouod be yes


meet_reqs2(x)

```



```{r}

valid_passwords %>%
  select(-valid_pwd) %>% 
  mutate(valid_pwd = map(value, meet_reqs2)) %>% 
  unnest() %>% 
  filter(valid_pwd == 1) %>% 
  count(valid_pwd)

```


